Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-19 prob.tex
prob.tex \section{Proofs} Found an idea of proof doesn't really work...
prob.tex \section{Proofs} Keep fixing the proof...>"<
prob.tex \section{Proofs} Still stuck... Consider to construct some examples...

\begin{lemma}\label{lemma:analogGeometricInterludeRichmanBridges1999}Let
\[
n\left(\theta\right)=\begin{cases}
7 & \textrm{, if }\cos\theta\le\frac{1}{32}\textrm{ ;}\\
k+2 & \textrm{, if }\frac{1}{2^{k-1}}<\cos\theta\le\frac{1}{2^{k}}\textrm{ for }k\ge6\textrm{ .}
\end{cases}
\]
If $\ket{\psi}$ and $\ket{\psi'}$ are points in the northern hemisphere
with the same latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$,
and the difference of their longitude is $a$, then we could takes
at least $n\left(\theta\left(\ket{\psi}\right)\right)$ close steps
along East-West great circles to go from $\ket{\psi'}$ to a point
$\ket{\psi_{s}}$ due south of $\ket{\psi}$. When taking $n\ge n\left(\theta\left(\ket{\psi}\right)\right)$
steps, the latitude will go down by at most $\frac{a^{2}}{n}$.\qed\end{lemma}
\begin{proof}
...........................
\end{proof}
The following theorem is an analog to Lemma~20 in \cite{RichmanBridges1999}.

@@

\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
\begin{itemize}
\item Let $f:S^{2}\rightarrow\mathbb{R}$ be a bounded continuous approximation
frame function of weight~$\left(W_{l},W_{r}\right)$, $W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$.\qed\end{thm}
\begin{proof}
Let $\ket{\bar{2}}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{\bar{0}}$.
Then 
\[
\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{\bar{0}}\right)+f\left(\ket{\bar{2}}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{\bar{2}}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{\bar{0}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
denote the coordinates of a point~$\ket{\psi}$ with respect to the
frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.

@@

\yutsung{\begin{thm}\label{thm:analogTheorem3.5Gleason1957}~
\begin{itemize}
\item Let $f:\mathbb{C}S^{2}\rightarrow\mathbb{R}$ be a bounded continuous
approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$. Recall $f$ could be uniquely extended
to the whole space~$\mathbb{C}^{3}$ by $f\left(0\right)=0$ and
$f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
for nonzero vector~$\ket{\psi}$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{2}$.\qed\end{thm}}

\yutsung{
\begin{proof}
~

\begin{claim}~
\begin{itemize}
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=\bra{\psi}\left[M\proj{0}+\left(W-M-m\right)\proj{1}+m\proj{2}\right]\ket{\psi}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
\begin{proof}
For all vector~$\ket{\psi}\in\mathbb{C}S^{1}$, 
\begin{eqnarray*}
 &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
 & = & \left|Q\left(\ket{\psi}\right)-f\left(\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\sum_{i=1}^{2}\ket{i}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{i}{\psi}}{\left|\ip{i}{\psi}\right|}\left|\ip{i}{\psi}\right|\right)\right|
\end{eqnarray*}
In order to estimate the last equation, we need to verify the conditions
listed in theorem~\ref{thm:analogTheorem23RichmanBridges1999}.

First, $\ket{0}$, $\ket{1'}=\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}$,
and $\ket{2'}=\ket{2}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{2}{\psi}}{\left|\ip{2}{\psi}\right|}$
form an orthonormal basis, and the restriction of $f$ on the real
vector space spanned by $\ket{0}$, $\ket{1'}$, and $\ket{2'}$ is
still a approximation frame function of weight~$\left(W_{l},W_{r}\right)$.
Because $f\left(\ket{0}\right)=M$, we must also have $f\left(\ket{0}\right)=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$. 
\end{proof}
\end{proof}
}

\yutsung{
\begin{proof}
~
\begin{proof}
This proof will be separated into two parts. The first part will estimate
the error between the approximation frame function and the quadratic
form on every complex two-space. The second part will then verify
the quadratic forms in the first part could be connected and get a
quadratic form on the whole space.
\end{proof}
\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 
\begin{itemize}
\item Consider the complex vector space spanned by $\ket{\psi_{0}}$ and
$\ket{\psi_{1}}$, and $\mathbb{C}S^{1}$ be its unit sphere, i.e.,
\[
\left\{ \alpha_{0}\ket{\psi_{0}}+\alpha_{1}\ket{\psi_{1}}\middle|\alpha_{0},\alpha_{1}\in\mathbb{C}\textrm{ and }\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=1\right\} \textrm{ .}
\]
\item $\ket{\psi_{2}}=\ket{\psi_{0}}\times\ket{\psi_{1}}\in\mathbb{C}S^{2}$.
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
\item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{claim}
\end{proof}
}

>>>>

\begin{lemma}\label{lemma:analogGeometricInterludeRichmanBridges1999}Let
\[
n\left(\theta\right)=\begin{cases}
7 & \textrm{, if }\cos\theta\le\frac{1}{32}\textrm{ ;}\\
k+2 & \textrm{, if }\frac{1}{2^{k-1}}<\cos\theta\le\frac{1}{2^{k}}\textrm{ for }k\ge6\textrm{ .}
\end{cases}
\]
If $\ket{\psi}$ and $\ket{\psi'}$ are points in the northern hemisphere
with the same latitude~$\theta\left(\ket{\psi}\right)=\theta\left(\ket{\psi'}\right)$,
and the difference of their longitude is $a$, then we could takes
at least $n\left(\theta\left(\ket{\psi}\right)\right)$ close steps
along East-West great circles to go from $\ket{\psi'}$ to a point
$\ket{\psi_{s}}$ due south of $\ket{\psi}$. When taking $n\ge n\left(\theta\left(\ket{\psi}\right)\right)$
steps, the latitude will go down by at most $\frac{a^{2}}{n}$.\qed\end{lemma}
\begin{proof}
\yutsung{{To be typed...}}
\end{proof}
The following theorem is an analog to Lemma~20 in \cite{RichmanBridges1999}.

@@

\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
\begin{itemize}
\item Let $f:S^{2}\rightarrow\mathbb{R}$ be a bounded continuous approximation
frame function of weight~$\left(W_{l},W_{r}\right)$, $W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{0}$.
\item Choose $\ket{1}\in S^{2}$ such that $\ip{1}{0}=\ip{1}{2}=0$. For
example, we may choose $\ket{1}=\ket{2}\times\ket{0}$.
\item $Q\left(\ket{\psi}\right)=M\ip{\psi}{0}\ip{0}{\psi}+\left(W-M-m\right)\ip{\psi}{1}\ip{1}{\psi}+m\ip{\psi}{2}\ip{2}{\psi}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$.\qed\end{thm}
\begin{proof}
Let $\ket{\bar{2}}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{\bar{0}}$.
Then 
\[
\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{\bar{0}}\right)+f\left(\ket{\bar{2}}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{\bar{2}}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{\bar{0}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
denote the coordinates of a point~$\ket{\psi}$ with respect to the
frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.

@@

\yutsung{\begin{thm}\label{thm:analogTheorem3.5Gleason1957}~
\begin{itemize}
\item Let $f:\mathbb{C}S^{2}\rightarrow\mathbb{R}$ be a bounded continuous
approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$. Recall $f$ could be uniquely extended
to the whole space~$\mathbb{C}^{3}$ by $f\left(0\right)=0$ and
$f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
for nonzero vector~$\ket{\psi}$.
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{\psi}{0}\ip{0}{\psi}+\left(W-M-m\right)\ip{\psi}{1}\ip{1}{\psi}+m\ip{\psi}{2}\ip{2}{\psi}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{2}$.\qed\end{thm}}

\yutsung{
\begin{proof}
For every vector~$\ket{\psi}\in\mathbb{C}S^{1}$, consider the real
vector space spanned by $\ket{0'}=\lambda_{0}\ket{0}$, $\ket{\bar{0}'}=\lambda_{\bar{0}}\ket{\bar{0}}$,
$\ket{\psi'}=\lambda_{\psi}\ket{\psi}$, where $\lambda_{0}$, $\lambda_{\bar{0}}$,
and $\lambda_{\psi}\in\mathbb{C}$, and denote its unit sphere as
$S^{2}$. Then, 
\begin{eqnarray*}
f\left(\ket{0'}\right)=f\left(\ket{0}\right)=\max_{\ket{\phi}\in\mathbb{C}S^{2}}f\left(\ket{\phi}\right)\ge\max_{\ket{\phi}\in S^{2}}f\left(\ket{\phi}\right)\ge f\left(\ket{0'}\right) & \Rightarrow & \max_{\ket{\phi}\in S^{2}}f\left(\ket{\phi}\right)=f\left(\ket{0'}\right)\\
f\left(\ket{\bar{0}'}\right)=f\left(\ket{\bar{0}}\right)=\min_{\ket{\phi}\in\mathbb{C}S^{2}}f\left(\ket{\phi}\right)\le\min_{\ket{\phi}\in S^{2}}f\left(\ket{\phi}\right)\le f\left(\ket{\bar{0}'}\right) & \Rightarrow & \min_{\ket{\phi}\in S^{2}}f\left(\ket{\phi}\right)=f\left(\ket{\bar{0}'}\right)\textrm{ .}
\end{eqnarray*}
And let 
\begin{eqnarray*}
\ket{2'} & = & \sigma_{\ket{0'}\times\ket{\bar{0}'}}\ket{0'}=\frac{\left[\left(\lambda_{0}\ket{0}\right)\times\left(\lambda_{\bar{0}}\ket{\bar{0}}\right)\right]\times\left(\lambda_{0}\ket{0}\right)}{\left\Vert \left[\left(\lambda_{0}\ket{0}\right)\times\left(\lambda_{\bar{0}}\ket{\bar{0}}\right)\right]\times\left(\lambda_{0}\ket{0}\right)\right\Vert }=\frac{\lambda_{0}\lambda_{\bar{0}}\lambda_{0}^{*}\left[\left(\ket{0}\times\ket{\bar{0}}\right)\times\left(\ket{0}\right)\right]}{\left\Vert \lambda_{0}\lambda_{\bar{0}}\lambda_{0}^{*}\left[\left(\ket{0}\times\ket{\bar{0}}\right)\times\left(\ket{0}\right)\right]\right\Vert }=\sigma_{\ket{0}\times\ket{\bar{0}'}}\ket{0}\frac{\lambda_{\bar{0}}}{\left|\lambda_{\bar{0}}\right|}=\ket{2}\frac{\lambda_{\bar{0}}}{\left|\lambda_{\bar{0}}\right|}
\end{eqnarray*}
Is $\ket{0}\times\ket{\bar{0}'}\in S^{2}$? Can't we find a rotate
$\ket{0'}$ in $S^{2}$? And then $\ket{2'}$ will be obviously in
$S^{2}$? Then, the problem will be whether $\ket{2'}$ parallel to
$\ket{2}$? Use Mathematica to compute some example?
\begin{eqnarray*}
 &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
 & = & \left|Q\left(\ket{\psi}\right)-f\left(\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\sum_{i=1}^{2}\ket{i}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{i}{\psi}}{\left|\ip{i}{\psi}\right|}\left|\ip{i}{\psi}\right|\right)\right|
\end{eqnarray*}
In order to estimate the last equation, we need to verify the conditions
listed in theorem~\ref{thm:analogTheorem23RichmanBridges1999}.

First, $\ket{0}$, $\ket{1'}=\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}$,
and $\ket{2'}=\ket{2}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{2}{\psi}}{\left|\ip{2}{\psi}\right|}$
form an orthonormal basis, and the restriction of $f$ on the real
vector space spanned by $\ket{0}$, $\ket{1'}$, and $\ket{2'}$ is
still a approximation frame function of weight~$\left(W_{l},W_{r}\right)$.
Because $f\left(\ket{0}\right)=M$, we must also have $f\left(\ket{0}\right)=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$. 
\end{proof}
}
